Environmental stress drives intermediate plant and pollinator specialisation

### 2020-05-12 paper/manuscript.Rmd
Add refs for occurrence cleaning

After obtaining information about species occurrence and the environment, we then merged these two datasets such that a vector with details of our 37 bioclimatic and topographic variables characterised the location of each occurrence. 
Sets of occurrence data tend to be spatially aggregated due to sample bias (tendency to collect close to cities, certain countries). 
Moreover, spatial autocorrelation arises in ecological data because geographically clumped records tend to be more similar in physical characteristics and/or species abundances than do pairs of locations that are farther apart. 
To account for such spatial dependency in occurrence data, we only included one occurrence record if a species had more than one within a cell of the bioclimatic raster. 
We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrence records collected opportunistically as the ones we use here. 
In this step we removed `r scales::percent(percent_thinned)` of the occurrences which resulted in a total of `r round(sum(n_thinned_occurrences$N)/1000000, digits = 1)` million occurrences used in our niche analysis.

A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not precisely match the landmass boundaries. 
The result of this missmatch is that not all environmental variables were available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total). 
As expected, the vast majority of these problematic cells were close to the shore. 
To address this issue, we calculated the average value of environmental variables within a `r config$climate_buffer/1000`km buffer of the centre of the cell where the variable was missing and used it to approximate the value of the variable in that cell. 
Using this procedure, we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells where they were missing. 
To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but instead using a `r config$climate_buffer*2/1000`km buffer. 
We removed from further analysis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables (`r scales::percent(complete_filled_cells_2[1]/sum(complete_filled_cells_2), 0.01)` of the total).

>>>>

After obtaining information about species occurrence and the environment, we then merged these two datasets such that a vector with details of our 37 bioclimatic and topographic variables characterised the location of each occurrence. 
Sets of occurrence data tend to be spatially aggregated due to sample bias [tendency to collect close to cities, certain countries; @jetz_essential_2019]. 
Moreover, spatial autocorrelation arises in ecological data because geographically clumped records tend to be more similar in physical characteristics and/or species abundances than do pairs of locations that are farther apart [@elith_species_2009; @dormann_methods_2007]. 
To account for such spatial dependency in occurrence data, we only included one occurrence record if a species had more than one within a cell of the bioclimatic raster [@torres_using_2018; @elith_species_2009]. 
We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrence records collected opportunistically as the ones we use here. 
In this step we removed `r scales::percent(percent_thinned)` of the occurrences which resulted in a total of `r round(sum(n_thinned_occurrences$N)/1000000, digits = 1)` million occurrences used in our niche analysis.

A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not precisely match the landmass boundaries [@zizka_coordinatecleaner_2019]. 
The result of this missmatch is that not all environmental variables were available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total). 
As expected, the vast majority of these problematic cells were close to the shore. 
To address this issue, we calculated the average value of environmental variables within a `r config$climate_buffer/1000`km buffer of the centre of the cell where the variable was missing and used it to approximate the value of the variable in that cell. 
Using this procedure, we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells where they were missing. 
To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but instead using a `r config$climate_buffer*2/1000`km buffer. 
We removed from further analysis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables (`r scales::percent(complete_filled_cells_2[1]/sum(complete_filled_cells_2), 0.01)` of the total).
